Supplementary Figures and Tables

### 2020-11-13 Supplementary_fig_tab.Rmd
mir30a figure

>>>>

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.width=5, fig.height=5, fig.show='hold', fig.cap = "Log2 transformed expression level of miR-30a-5p in tumor and normal tissue samples of 87 patients."}

matched_patient_miRNA_exp_dataset <- readRDS("figure_manuscript/matched_patient_miRNA_exp_dataset.RDS")

significant_mirna_nodes <- readRDS("figure_manuscript/significant_mirna_nodes.RDS")

matched_patient_miRNA_exp_dataset%>%
  filter(miRNA %in% significant_mirna_nodes)%>%
  filter(miRNA == "hsa-miR-30a-5p")%>%
  pivot_longer(cols = contains("TCGA"), 
               names_to = "patient_id", 
               values_to = "expressions") %>%
  mutate(patient = ifelse(endsWith(patient_id, "01A"), 
                          "tumor", "normal")) %>%
  group_by(patient, miRNA) %>%
  ggplot(aes(x = miRNA, y = log2(expressions), fill = patient)) +
  # scale_y_log10()+
  geom_boxplot(position = "dodge") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90), 
        panel.background = element_rect(),
        legend.title = element_blank()) +
  xlab("")
